---
title: "Quarto Computations"
format: 
  html: 
    code-link: true
    df-print: paged
---

This dataset contains a subset of the fuel economy data from the EPA. Specifically, we use the `mpg` dataset from the **ggplot2** package.

```{r}
#| label: load-packages

library(ggplot2)
```

Here is the cars data:

```{r}
#| label: tbl-mpg
#| tbl-cap: "The cars data"
#| column: page
mpg
```

::: callout-note
There are some graphs coming.
:::

```{r}
#| label: fig-mpg
#| fig-cap: "City and highway mileage for 38 popular models of cars."
#| fig-subcap:
#|   - "Color by number of cylinders"
#|   - "Color by engine displacement, in liters"
#| layout-ncol: 2
#| column: page

ggplot(mpg, aes(x = hwy, y = cty, color = cyl)) +
  geom_point(alpha = 0.5, size = 2) +
  scale_color_viridis_c() +
  theme_minimal()

ggplot(mpg, aes(x = hwy, y = cty, color = displ)) +
  geom_point(alpha = 0.5, size = 2) +
  scale_color_viridis_c(option = "E") +
  theme_minimal()
```

The plots in @fig-mpg show the relationship between city and highway mileage for 38 popular models of cars. The original dataset is shown in @tbl-mpg. In @fig-mpg-1 the points are coloured by the number of cylinders while in @fig-mpg-2 the points are coloured by engine displacement.
